

%-------------------------
% Resume in LaTeX
% Author : Mahmoud Zourob (dot bullets + spacing + subheading alignment)
%-------------------------

\documentclass[letterpaper,11pt]{article}

% Packages
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

% Page setup
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\tabcolsep}{0in}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Resume items
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}

% ---- Subheading alignment fix ----
% Left column: shifted left by 1em
% Right column: shifted left by 0.5em (brings it closer to center)
\newcommand{\resumeSubheading}[4]{%
  \vspace{-1pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} -- #3 & #2 \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{@{\hspace{-1em}}l@{\extracolsep{\fill}}r@{\hspace{-0.5em}}}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-5pt}
}

% ---- List formatting ----

% 1. EXPERIENCE LIST (Left margin 0in)
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

% 2. PROJECT LIST (Left margin 0.15in)
\newcommand{\resumeProjectListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeProjectListEnd}{\end{itemize}}

% 3. EXPERIENCE BULLETS (Standard indent: 0in + 0.2in = 0.2in absolute)
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.4in, label=\textbullet, labelsep=1em]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% 4. PROJECT BULLETS (Reduced indent: 0.15in + 0.05in = 0.2in absolute)
\newcommand{\resumeProjectItemListStart}{\begin{itemize}[leftmargin=0.25in, label=\textbullet, labelsep=1em]}
\newcommand{\resumeProjectItemListEnd}{\end{itemize}\vspace{-5pt}}

% ---- Global bullet style ----
\setlist[itemize]{label=\textbullet, labelsep=0.6em}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}


%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape MAHMOUD ZOUROB} \\ \vspace{1pt}
    \small (+1) 343-996-4771 $|$ 
    \href{mailto:mahmoudzourob13@gmail.com}{\underline{email}} $|$ 
    \href{www.linkedin.com/in/mahmoud-zourob-24401829b}{\underline{linkedin.com/mahmoud}} $|$ 
    \href{https://github.com/mmdoo7123}{\underline{Github}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{University of Ottawa} & Ottawa, ON \\
    \textit{Bachelor of Computer Engineering:} &  \textbf{Graduating April 2027} \\
\end{tabular*}
\textbf{Coursework:} Computer Architecture; Digital Systems ; Signal and System Analysis; Computer Systems Design; Principles and Applications of VLSI Design; Data Communications and Networking


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {EcoSafeSense}{Jan 26' -- Present}
  {Solar Charge Controller Configuration Engineer}{}
\resumeItemListStart
  \resumeItem{Improved solar charging efficiency by \textbf{~30\%} using a \textbf{TI BQ25798} buck-boost charger with integrated \textbf{MPPT} and NVDC power-path control.}
  \resumeItem{Configured charger operation via \textbf{I\textsuperscript{2}C register tuning} and validated performance using bench PSU testing and real-time V/I power measurements.}
  \resumeItem{Built firmware-ready battery charge profiles using measured system load data (\textbf{157 mW baseline}) for reliable cold-weather embedded operation.}
\resumeItemListEnd


\resumeSubheading
  {National Research Council}{May 25' -- Aug 25'}
  {Automation Engineer Intern}{}
\resumeItemListStart
  \resumeItem{Implemented hardware process control for DIW electrode fabrication using \textbf{Hyrel 30M}, \textbf{Repetrel}, and \textbf{PrusaSlicer}, tuning deposition parameters for repeatable electrochemical performance.}
  \resumeItem{Built data-driven optimization pipelines using \textbf{Python/MATLAB} to process electrochemical test data and model microstructure–performance relationships.}
  \resumeItem{Performed hardware validation using battery cyclers and potentiostat instrumentation, achieving \textbf{125 mAh/cm\textsuperscript{2}} LMNO half-cell performance with reduced electrolyte overhead.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeProjectListStart

\resumeProjectHeading
  {{\textbf{\textbf{UART Design}}} $|$ \emph{ASM, FSM design, VHDL, Digital Systems, RTL Design}}{}
\resumeItemListStart
  \resumeItem{Designed a fully functional UART transmitter and receiver using FSM/ASM control logic.}
  \resumeItem{Implemented RTL-level digital systems in VHDL, following strict structural design constraints.}
  \resumeItem{Integrated baud rate generation, shift registers, and control/status registers.}
\resumeItemListEnd

\resumeSubheading
  {uOttawa Supermileage -- Electrical Team}{}
  {Embedded Systems \& Telemetry Engineer}{}
\resumeItemListStart
  \resumeItem{Designed and implemented a real-time telemetry system to collect, transmit, and visualize vehicle performance data (speed, RPM, battery voltage).}
  \resumeItem{Integrated sensors and microcontrollers (Arduino, ESP32) with CAN bus communication for vehicle diagnostics and system monitoring.}
  \resumeItem{Optimized power management and signal integrity across the electrical system to meet energy-efficiency competition constraints.}
\resumeItemListEnd


  \resumeProjectHeading
{{\textbf{VR Simulation on Autonomous Systems}} $|$ \emph{ Unity, C\#, Oculus SDK, VR Development}}{}
\resumeItemListStart
  \resumeItem{Engineered a Unity-based VR simulation highlighting challenges with autonomous systems.}
  \resumeItem{Integrated Oculus Quest, real-time audio synchronization, NPC behavior, and user feedback loops for enhanced realism and engagement.}
\resumeItemListEnd


\resumeProjectHeading
{{\textbf{Smart Home \& Garden Automation}} $|$ \emph{Arduino, C++, IoT, Sensors, Embedded Systems}}{}
\resumeItemListStart
  \resumeItem{Developed an Arduino-based system with integrated sensors (humidity, motion, rain, light) and actuators.}
  \resumeItem{Programmed in C++ using DHT11 libraries and optimized power management with Arduino WiFi.}
\resumeItemListEnd


\resumeProjectListEnd



%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
        \textbf{Languages:} C++, Python, VHDL, Verilog, C, C\# \\
        \textbf{Developer Tools:} Arduino IDE, Repetrel, PrusaSlicer, GitHub, Bench Power Instrumentation (PSU, Oscilloscope, Power Profiling) \\
        \textbf{Hardware/Embedded Platforms:} Arduino, Embedded Sensor Systems, Energy Harvesting Systems, Battery Management Systems (BMS), Solar MPPT Power Systems, DIW Manufacturing Systems (Hyrel 30M) \\
    }}
\end{itemize}
%-------------------------------------------
\end{document}
