%-------------------------
% Resume in Latex
% Author : Mahmoud Zourob
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Mahmoud Zourob}} & Email : \href{mailto:mahmoudzourob13@gmail.com}{mahmoudzourob13@gmail.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1(343)-996-4771 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Mahmoud Zourob} \\ \vspace{1pt}
    Ottawa, ON \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +1(343)-996-4771 ~ \href{mailto:mahmoudzourob13@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{mahmoudzourob13@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/mahmoud-zourob-24401829b?lipi=urn%3Ali%3Apage%3Ad_flagship3_profile_view_base_contact_details%3BQ%2BGufJQ6TKqZ0zACG2Eq6g%3D%3D}{\raisebox{-0.2\height}\faLinkedin\ \underline{mahmoud's linkedin}}  ~
    \href{https://github.com/mmdoo7123/}{\raisebox{-0.2\height}\faGithub\ \underline{https://github.com/mmdoo7123}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Ottawa}{Sep. 2023 -- Present}
      {Bachelor of Applied Science in Computer Engineering and Management Option}{Ottawa, ON}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Data Structures
                \item Software Methodology
                \item Algorithms Analysis
                \item Engineering Design
                \item Electronics
                \item Circuit Theory
                \item Software Construction
                \item Computer Architecture
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
	\resumeSubheading
		{National Research Council }{May 2025 -- Present}
		{Co-op Student Intern}{Ottawa, ON}
		\resumeItemListStart
			\resumeItem{3D printed custom porous electrodes using UV-curable resins and syringe-based extrusion with the Hyrel System 30M printer.}
			\resumeItem{Programmed and debugged G-code to coordinate UV curing and resin deposition with micro-scale precision.}
			\resumeItem{Collaborated with multidisciplinary teams to streamline battery testing workflows across electrical, chemical, and AI domains.}
	\resumeItemListEnd

    \resumeSubheading
      {KFUPM(King Fahd University of Petroleum and Minerals) }{October 2024 -- February 2025}
      {GSR Conference International Student Ambassador}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Tracked and reported on the representation and activities of GSR, including numbers and progress.}
        \resumeItem{Built connections with international peers, decision-makers, and academic leaders.}
        \resumeItem{Advocated for the GSR Ambassadors Program and the conference as a whole within Ontario. }
        \resumeItem{Motivated students to engage with GSR by submitting their research papers and participating in events.}
      \resumeItemListEnd

    \resumeSubheading
      {BloomKSA}{Sept 2022 -- May 2023}
      {Model United Nations (MUN) Chief of Operations}{Riyadh, Saudi Arabia}
      \resumeItemListStart
        \resumeItem{Oversaw committee management and supervise operational staff to ensure effective session handling.}
        \resumeItem{Managed logistics and delegate support for smooth MUN conference operations.}
        \resumeItem{Handled crises, collaborated with the Secretariat, and gathered feedback for continual improvement of MUN 
        	conference.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart 
          
		   \resumeProjectHeading
				{\textbf{AI-Driven Market Research Assistant} $|$ \emph{Python, NLP, React, Plotly, GCP, Docker}}{May 2024}
				\resumeItemListStart
				\resumeItem{Developed a tool leveraging NLP and sentiment analysis to extract trends and customer insights from social media and news.}
				\resumeItem{Built scalable scrapers, and interactive dashboards, and deployed them on AWS with Docker.}
		 	\resumeItemListEnd
		 	
			  \vspace{-13pt}
	          \resumeProjectHeading
	          {\textbf{Financial Analysis \& Profit Prediction Model} $|$ \emph{Python, ARIMA, Pandas, API Integration}}{December 2024}
	          \resumeItemListStart
	          \resumeItem{Building Forecasting Tools with ARIMA, API Integration, 
	          	and Python to predict profit growth and provide financial insight based on balance sheets and income statements.}
          \resumeItemListEnd 
          
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Service Rental Application} $|$ \emph{Java, Android Studio, Firebase, XML}}{November 2024}
          \resumeItemListStart
          \resumeItem{Built Rentify, a scalable Android app for item rentals, featuring role-based 
          	access (Admin, Lessor, Renter).}
          \resumeItem{ Utilized Java, XML, and Firebase for real-time databases, authentication, and 
          	streamlined rental management, including item listings and requests.}
          \resumeItemListEnd  
		  
		    \vspace{-13pt}
		  \resumeProjectHeading
		  {\textbf{VR Simulation on Autonomous Systems} $|$ \emph{Unity, C\#, Oculus SDK, VR Development}}{December 2023}
		  \resumeItemListStart
		  \resumeItem{Engineered a Unity-based VR simulation highlighting challenges with autonomous systems.}
		  \resumeItem{ Integrated Oculus Quest, real-time audio synchronization, NPC behavior, and 
		  	user feedback loops for enhanced realism and engagement.}
		  \resumeItemListEnd
		  
		  \vspace{-13pt}
		  \resumeProjectHeading
		  {\textbf{University Login Portal \& Meetings App} $|$ \emph{Java, Android Studio, PostgreSQL, Swing}}{November 2023}
		  \resumeItemListStart
		  \resumeItem{Developed a secure, scaleable application using Java, PostgreSQL, and Swing.}
		  \resumeItem{Implemented role-based authentication, dynamic CRUD operations, meeting scheduling, 
		  	and optimized search and sort algorithms with real-time database integration.}
		  \resumeItem{Utilized the layout editor to create a UI for the application in order to allow different scenes to interact with each other.}
		  \resumeItemListEnd 
		  
		  \resumeProjectHeading
		  {\textbf{Smart Home \& Garden Automation} $|$ \emph{Arduino, C++, IoT, Sensors, Embedded Systems}}{May 2023}
		  \vspace{-13pt}
		  \resumeItemListStart
		  \resumeItem{Developed an Arduino-based system with integrated sensors (humidity, motion, rain, light) and actuators. }
		  \resumeItem{Programmed in C++ using DHT11 libraries and optimized power 
		  	management with Arduino WiFi.}
		  
		  \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C++, C\#, SQL, XML, HTML, CSS, JavaScript} \\
     \textbf{Developer Tools}{:  Android Studio, Jetpack Compose, JFrame, Unity, Firebase, API 
     	Integration, Google Cloud Platform, Docker} \\
	 \textbf{Technologies/Frameworks}{: GitHub, Jenkins, Unity, WordPress, Firebase, Arduino, PrusaSlicer, Android SDK, GCP, Selenium WebDriver}

    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Leadership / Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{Palestinian Student Association}{Fall 2024 -- Present}{Events Executive member}{University of Ottawa}
            \resumeItemListStart
                \resumeItem{Achieved 2nd place in Cultural Club of the Year at the annual Student Life Awards.}
                \resumeItem{Collaborating 20+ members creating events ideas and plan their execution to improve and promote community engagement, advocating, and unity.}
            \resumeItemListEnd
            
        \resumeSubheading{Uottawa Supermileage}{Fall 2023 -- Summer 2024}{Electrical Team}{University of Ottawa}
        	\resumeItemListStart
				\resumeItem{Designed and implemented a real-time telemetry system to collect, transmit, and visualize vehicle performance data (e.g., speed, RPM, battery voltage).}
				\resumeItem{Integrated sensors and microcontrollers (e.g., Arduino, ESP32) with CAN bus communication to support efficient vehicle diagnostics.}
				\resumeItem{Collaborated with mechanical and software subteams to align sensor placements and data formats with aerodynamic and control system requirements.}
				\resumeItem{Optimized power management and signal integrity across the electrical system to meet energy efficiency competition constraints.}
        \resumeItemListEnd
        
    \resumeSubHeadingListEnd


\end{document}
